%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{deedy-resume-openfont}


\begin{document}
\topmargin = -40pt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Jasneet Singh}{Sawhney}{ \urlstyle{same}\url{https://www.linkedin.com/in/jasneet-singh-sawhney-707944110/} \\ {aashitsingh2010@gmail.com |+91-9136890018| \\ WZ-286A, 1st Floor, Rishi Nagar, Rani Bagh, Delhi - 110034}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{Northern India \\ Engineering College}
\descript{B.Tech in Electronics and Communication}
\location{Expected May 2020 |\\ New Delhi, India \\ GPA (first year) : 8.8}
\sectionsep
\vspace{3mm}
\subsection{C.R.P.F. PUBLIC SCHOOL}
\descript{HIGHER SECONDARY EDUCATION-CBSE}
\location{Aggregate : 82.00\% \\ Passing Year : 2016 }
\sectionsep

\descript{SENIOR SECONDARY EDUCATION-CBSE}
\location{CGPA : 9.2/10 \\ Passing Year : 2016 }
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep
\section{Links} 
Github:// \href{https://github.com/InnovativeCoder}{\custombold{InnovativeCoder}} \\
LinkedIn://  \href{https://www.linkedin.com/in/jasneet-singh-sawhney-707944110/}{\custombold{jasneetsinghsawhney}} \\
YouTube://  \href{https://www.youtube.com/channel/UCKQOUcqLLQXWLKUAQbfKiNQ}{\custombold{Innovative Coder}} \\
Quora://  \href{https://www.quora.com/profile/Jasneet-Singh-Sawhney}{\custombold{Jasneet-Singh-Sawhney}}
Instagram:// \href{https://www.instagram.com/innovative_coder/}{\custombold{innovativecoder}}
\sectionsep
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{TECHNICAL SKILL SET}

\subsection{Programming languages}
\descript{C, C++, Python, \LaTeX\ }
\sectionsep

\subsection{Software packages}
\descript{Tensorflow, OpenCV, Numpy, Pandas, nltk, matplotlib, sklearn}
\sectionsep

\subsection{Operating systems}
\descript{Mac-OS, Ubuntu, MS-Windows}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\setlength{\columnsep}{1in}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.60\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience }


\runsubsection{IEEE}
\descript{| Xtreme Ambassador }

\location{Aug 2017 ? Oct 2017 | New Delhi, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item  Promote Xtreme 11.0 in my own college and other colleges.\item Directly worked under Mr. Prasanth Mohan, program chair of IEEE Xtreme, a competitive coding 24 hours hackathon. \item Completed all the assigned tasks. %\item Also got a LOR from Prasanth Sir.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{EightLeggedGeeks}
\descript{| Winner of Zoohackathon by US embassy and WWF}

The Web App meant to scrape all the tweets with a particular query and analyse its suspiciousness. All tweets are given a score, as per pre-decided features, to determine the tweets; most likely used in wildlife trade. Finally, most likely tweets, with score>2, are returned and the net percentage of such tweets are described on a pie-chart.
\sectionsep

\runsubsection{Smartspi}\descript{|2\textsuperscript{nd} Prize at hach@bvp}
Project made during 24 hours long hackathon at Bharati Vidyapeeth College of Engineering. An android app, having multiple features, controlling lock with mobile's fingerprint sensor, controlling A/C from mobile, mood lighting control, and prediction for installation of Air Purifier.\\ Presenatation link - https://devpost.com/software/smarthabitat
\sectionsep

\runsubsection{TicTacToe AI}
Project uses reinforcement learning as its base. Computer learns the move from user to train itself and gets better with each game.
\sectionsep

\runsubsection{Face Recognition}
Project uses OpenCV and KNN at backend. OpenCV is used to detect face using Cascade classifier and K nearest nieghbours algorithm is used to classify the data for recognition of face.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2017	     & Winner out of 11 teams & Zoohackathon 2017 
\\ &&by WWF and US embassy\\
2017	     & 2\textsuperscript{nd} Position out of 25 teams & hack@bvp 2017 

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies} 

\begin{tabular}{rll}
2017 - Present 	&   International & IEEE \\
2017 - Present   & Intra-College   & Source : Data Science Society

\end{tabular}
\sectionsep

\end{minipage} 

\end{document}